### 2014-04-30 Rcode/intro.rmd
update intro.rmd to replace localfdr with lfdr

#This code mostly borrowed from the examples in mixFdr in R help
m=beta.mfdr.J15
mTrue = list(pi=c(0.8,0.2),mu=c(0,0),sig=c(1,2))
par(mfcol=c(1,1))
s = seq(-5,5,by=0.01)
trueFdr = fdrMixModel(s,mTrue,c(TRUE,FALSE))
fdrCurve = fdrMixModel(s,m,abs(m$mu - m$mu[1])<=0.002) # this tells it which indices to consider null
 plot(s, trueFdr, t = 'l', main = "fdr - Black is true", xlab = "z", ylab = "fdr", ylim = c(0,1))
 lines(s, fdrCurve, col = 2)
points(ss$betahat,beta.ash$localfdr,col=3)
points(ss$betahat,beta.ash.u$localfdr,col=4)
points(ss$betahat,beta.ash.hu$localfdr,col=5)

@@

z.ash = ash(z,1,mixcompdist="halfuniform")
points(z,z.ash$localfdr,col=3)
```

@@

```{r}
plot(beta.ash.auto$PosteriorMean, beta.ash$PosteriorMean, xlab="Shrunk estimate from auto method", ylab="Shrunk estimate from fixed method")
abline(a=0,b=1)
plot(beta.ash.auto$localfdr, beta.ash$localfdr, xlab="lfdr from auto method", ylab="ldfr from fixed method")
abline(a=0,b=1)

@@

[And VB method produces similar results to EM method]
```{r}
plot(beta.ash.auto$PosteriorMean, beta.ash.vb.uniform$PosteriorMean, xlab="Shrunk estimate from auto method", ylab="Shrunk estimate from vb method")
points(beta.ash.auto$PosteriorMean, beta.ash.vb.null$PosteriorMean, col=2)
abline(a=0,b=1)
plot(beta.ash.auto$localfdr, beta.ash.vb.uniform$localfdr, xlab="lfdr from auto method", ylab="ldfr from vb method")
points(beta.ash.auto$localfdr, beta.ash.vb.null$localfdr, col=2)
abline(a=0,b=1)

@@

It seems that in this case the ash q values underestimate the
FDR slightly. Possibly this is the assymetry.
Try shrinking positive and negatives separately:
```{r}
pos= betahat>0
betapos.ash=ash(betahat[pos],s[pos])
betaneg.ash = ash(betahat[!pos],s[!pos])
lfdr = rep(0,length(betahat))
lfdr[pos] = betapos.ash$localfdr
lfdr[!pos] = betaneg.ash$localfdr
qv = qval.from.localfdr(lfdr)
o = order(qv)
plot(cumsum(truenull[o])/(1:10000),qv[o],type="l")
abline(a=0,b=1)
```
No, that's not it.

>>>>

#This code mostly borrowed from the examples in mixFdr in R help
m=beta.mfdr.J15
mTrue = list(pi=c(0.8,0.2),mu=c(0,0),sig=c(1,sqrt(5)))
par(mfcol=c(1,1))
s = seq(-5,5,by=0.01)
trueFdr = fdrMixModel(s,mTrue,c(TRUE,FALSE))
fdrCurve = fdrMixModel(s,m,abs(m$mu - m$mu[1])<=0.002) # this tells it which indices to consider null
 plot(s, trueFdr, t = 'l', main = "fdr - Black is true", xlab = "z", ylab = "fdr", ylim = c(0,1))
 lines(s, fdrCurve, col = 2)
points(ss$betahat,beta.ash$lfdr,col=3)
points(ss$betahat,beta.ash.u$lfdr,col=4)
points(ss$betahat,beta.ash.hu$lfdr,col=5)

@@

z.ash = ash(z,1,mixcompdist="halfuniform")
points(z,z.ash$lfdr,col=3)
```

@@

```{r}
plot(beta.ash.auto$PosteriorMean, beta.ash$PosteriorMean, xlab="Shrunk estimate from auto method", ylab="Shrunk estimate from fixed method")
abline(a=0,b=1)
plot(beta.ash.auto$lfdr, beta.ash$lfdr, xlab="lfdr from auto method", ylab="ldfr from fixed method")
abline(a=0,b=1)

@@

[And VB method produces similar results to EM method]
```{r}
plot(beta.ash.auto$PosteriorMean, beta.ash.vb.uniform$PosteriorMean, xlab="Shrunk estimate from auto method", ylab="Shrunk estimate from vb method")
points(beta.ash.auto$PosteriorMean, beta.ash.vb.null$PosteriorMean, col=2)
abline(a=0,b=1)
plot(beta.ash.auto$lfdr, beta.ash.vb.uniform$lfdr, xlab="lfdr from auto method", ylab="ldfr from vb method")
points(beta.ash.auto$lfdr, beta.ash.vb.null$lfdr, col=2)
abline(a=0,b=1)

@@

It seems that in this case the ash q values underestimate the
FDR slightly. Possibly this is the assymetry.
Try shrinking positive and negatives separately:
```{r}
pos= betahat>0
betapos.ash=ash(betahat[pos],s[pos])
betaneg.ash = ash(betahat[!pos],s[!pos])
lfdr = rep(0,length(betahat))
lfdr[pos] = betapos.ash$lfdr
lfdr[!pos] = betaneg.ash$lfdr
qv = qval.from.localfdr(lfdr)
o = order(qv)
plot(cumsum(truenull[o])/(1:10000),qv[o],type="l")
abline(a=0,b=1)
```
No, that's not it.
